Hochschild cohomology of torus-equivariant D-modules

### 2017-05-30 paper.tex
Fixed proof of the main theorem.

@@

@@

\begin{Thm}
    \label{thm:torus:is-good}%
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then the stack $\stack X = X/G$ is good.
\end{Thm}

Together with Theorem~\ref{thm:good-is-good} this implies our main result, Theorem~\ref{thm:main}.

\begin{Rem}
    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
    Thus it would suffice to assume that $X$ can be covered by open subschemes for which Lemma~\ref{lem:finitely_many_stabilizers} holds.
\end{Rem}

\begin{Rem}
    Theorem~\ref{thm:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
    The argument is exactly the same.
\end{Rem}

By Lemma~\ref{lem:base-change:cover}, it suffices to prove Theorem~\ref{thm:torus:is-good} for stacks $X/G$ with $X$ affine.
We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the partial compactification $\Gm^n \subseteq \as n$.
To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.

We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working directly with the stacks, we can base change to schemes.
We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ and the primes from the maps.
\dropprimes%
Thus we are concerned with the diagram
\[
    \begin{tikzcd}
        \schemelscY \stack X \arrow[r, hook, "\schemei"] &
        \schemeclsY \stack X \arrow[r, "\schemebarq"] &
        \bar Γ &
        Γ \arrow[l, hook', "\schemej"'],
    \end{tikzcd}
\]
where we have to show that $\schemei^* \schemebarq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.

The general idea is to introduce a $\Gm$-action that contracts $\schemelscY \stack X$ onto $\schemeclsY \stack X$.
In order to do so, we will cut the scheme
\[
    \schemeclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
    \biggr\}
\]
into pieces according to the subgroups of $G$ that stabilize $\schemeh(y)$.
For this let $\Stab\stack X$ be the set of all closed subgroups of $G$ that are stabilizers of points of $X$, i.e.
\[
    \Stab\stack X = \{ G_x : x ∈ X \}.
\]

@@

\begin{proof}
    Since $X$ is affine, it can be embedded $G$-equivariantly into some $\as m$ with a linear $T$-action.
    For $\as m/T$ the statement is easy to see.
\end{proof}

Let $S$ be closed subgroup of $G$ and let $X^S$ be the $S$-fixed points of $X$.
Since $G$ is Abelian (and hence $S$ a normal subgroup), $X^S$ is a $G$-stable closed subscheme of $X$.
Hence $X^S/G$ is a closed substack of $\stack X$.
Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the closed subspace
\[
    \schemecls[S]_{\stack Y} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
    \biggr\}
    ⊆
    \schemecls_{\stack Y} \stack X.
\]

\begin{Lem}
    \label{lem:stabilizers_cover}%
    The subspaces $\schemecls[S]_{\stack Y} \stack X$ for $S ∈ \Stab\stack X$ cover $\schemecls_{\stack Y}\stack X$.
\end{Lem}

\begin{proof}
    Let $\schemelsY \stack X$ be the smooth cover of $\ls_{\stack Y}\stack X$.
    Consider the spaces
    \[
        \schemelsY[S] \stack X =
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ Γ \text{ and } g₂ ∈ g₁S
        \biggr\}
        \subseteq \schemelsY \stack X.
    \]
    The closure of $\schemelsY[S] \stack X$ in $\schemeclsY \stack X$ is exactly $\schemeclsY[S] \stack X$.
    It is easy to see that the subspaces $\schemelsY[S] \stack X$ for $S ∈ \Stab \stack X$ cover $\schemelsY[S] \stack X$.
    Now the statement follows from the fact that the closure of a finite union is the union of the individual closures.
\end{proof}

It will be useful to have a slight generalization of the schemes $\schemeclsY[S] \stack X$.
Let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$.
We set
\[
    \schemeclsY[S₁,S₂] \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
    \biggr\}.
\]
Clearly we have $\schemeclsY[S₁,S₂]{\stack X} \subseteq \schemecls[S₁]{\stack X}$ and $\schemeclsY[S] \stack X = \schemeclsY[S,S] \stack X$.

Consider the Cartesian square of closed embeddings
\[
    \begin{tikzcd}
        \schemelscY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}^c"] \arrow[d, hook, "\schemei^{S₁,S₂}"] & \schemelscY\stack X \arrow[d, hook, "\schemei"]
        \\
        \schemeclsY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}"]   & \schemeclsY\stack X
    \end{tikzcd}
\]

\begin{Lem}\label{lem:key_for_stablizier}%
    For any $S₁ ⊆ S₂$ in $\Stab\stack X$ and any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ we have
    \[
        \schemei^{S₁,S₂,*} α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F = 0.
    \]
\end{Lem}

\begin{proof}
    The scheme $\schemelsc[S₁,S₂] \stack X$ is given by
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
        \biggr\}.
    \]
    If $S₁ = \bar S₁$ the statement is trivially true.
    Otherwise the scheme $\bar S₁ \setminus S₁$ is the union of hyperplanes $H_i$ of $\bar S₁$.
    It suffices to prove the statement when further restricting to
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H_i
        \biggr\}.
    \]
    for all $i$.
    Let $H$ be one such hyperplane.
    We will assume that $H$ is contained in the closure of the connected component of $1 ∈ S₁$.
    The proof for $H$ in a different component is the same, up to a shift by an element of $G$.
    Let $\schemei_H$ be the inclusion of
    \[
        Z =
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H
        \biggr\}
    \]
    into $\schemeclsY[S₁,S₂] \stack X$.
    We want to compute
    \[
        (\schemei_H)^{*} α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F.
    \]
    We will do so be introducing a contractive $\Gm$-action on $\bar Γ$ and $\schemelsY[S₁,S₂]\stack X$ such that the morphism
    \[
        \schemebarq ∘ α_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ
    \]
    is $\Gm$-equivariant.

    We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
    This gives a corresponding decomposition of the monoid $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
    Let $H' = \bar G₁ H$.
    We note that $G ∩ H' = \emptyset$.

    We chose an action $μ$ of $\Gm$ on $\bar S₁$ that contracts $\bar S₁$ onto $H$.
    This induces an action of $\Gm$ on $\bar G = \bar G₁ \bar S₁$ by $u \cdot ts = tμ(u,s)$, contracting $\bar G$ onto $H'$.
    Further we obtain an action of $\Gm$ on $\bar Γ$ that keeps the first $X$ coordinate fixed.
    By construction this action contracts $\bar Γ$ onto a closed subvariety of $\bar Γ \setminus Γ$.
    We will denote this subvariety by $Z₁$ and the contraction morphism $π₁\colon \bar Γ → Z₁$ by $π₁$.

    We can also lift the action to $\schemeclsY[S₁,S₂]\stack X$ where it contracts onto $Z$.
    We will denote the corresponding contraction morphism by $π\colon \schemeclsY[S₁,S₂]\stack X → Z$.
    The morphism $\schemebarq ∘ α_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ$ is equivariant with respect to these $\Gm$-actions and on its image the action keeps the second $X$-coordinate fixed.

    We note that the D-modules $\schemej_!\sheaf F$ and $α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F$ are monodromic with respect to these $\Gm$-actions.
    Thus the contraction principle Theorem~\ref{thm:pre:contraction_principle} implies that
    \[
        (\schemei_H)^* α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F = π_* α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F.
    \]
    By construction, the square
    \[
        \begin{tikzcd}
            \schemecls[S₁,S₂] \stack X \arrow[r, "π"] \arrow[d, "\schemebarq ∘ α_{S₁,S₂}"] & Z \arrow[d] \\
            \bar Γ \arrow[r, "π₁"] & Z₁
        \end{tikzcd}
    \]
    is Cartesian.
    Let us call the right vertical map $f$.
    Base change yields
    \[
        π_* α_{S₁,S₂}^!\schemebarq^!\schemej_! \sheaf F =
        f^!π_{1,*} \schemej_! \sheaf F.
    \]
    Finally, let $i_{Z₁}\colon Z₁ \hookrightarrow \bar Γ$ be the inclusion.
    Applying the contraction principle again we obtain
    \[
        f^!π_{1,*} \schemej_! \sheaf F =
        f^!i_{Z₁}^* \schemej_! \sheaf F =
        0.
        \qedhere
    \]
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
    If $S₁,\, S₂ ∈ \Stab\stack X$, then
    \[
        \schemeclsY[S₁]\stack X ∩ \schemeclsY[S₂]\stack X =
        \schemeclsY[S₁∩S₂,\, S₁S₂].
    \]
    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemma~\ref{lem:key_for_stablizier}.
\end{proof}

>>>>

\newcommand\stabls[2]{L^{#1}#2}
\newcommand\stabcls[2]{\overline{L}^{#1}#2}
\newcommand\stablsc[2]{L^{#1,c}#2}
\newcommand\stablsY[3][\stack Y]{L_{#1}^{#2}#3}
\newcommand\stabclsY[3][\stack Y]{\overline{L}_{#1}^{#2}#3}
\newcommand\stablscY[3][\stack Y]{L_{#1}^{#2,c}#3}

@@

[$p₂$ <-> $p₁$]
[subvariety <-> subscheme]
[$Y₁$ <-> $Y₂$]
\dropprimes%
[macros]
[-advisor]
[map in contraction principle]

@@

\begin{Thm}
    \label{thm:torus:is-good}%
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then the stack $\stack X = X/G$ \isgoodb.
\end{Thm}

Together with Lemma~\ref{lem:base-change-criterion} and Proposition~\ref{prop:good-is-good} this implies our main result, Theorem~\ref{thm:main}.
Here by a \enquote{locally linear action} we mean that it is possible to cover $X$ by open $G$-stable subschemes $U_i$ such that each $U_i$ is $G$-equivariantly isomorphic to an open subscheme of some affine space $\as m$ with linear $G$-action.
This assumption is actually stricter than needed, see Remark~\ref{rem:why_locally_linear} below.

\begin{Rem}
    Theorem~\ref{thm:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
    The argument is exactly the same as in our case, but for the sake of keeping notational complexity down we will not present it here.
\end{Rem}

By Lemma~\ref{lem:base-change:cover}, it suffices to prove Theorem~\ref{thm:torus:is-good} for stacks $X/G$ with $X$ affine.
We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodnessb\ for the partial compactification $\Gm^n \subseteq \as n$.
To simplify notation, we drop the superscript $\as n$ from the notation and set $\bar{\stack X} = {}^{\as n}\bar{\stack X}$ and similarly for all other spaces and the various maps.
In other words, from now on all compactifications will implicitly be only with respect to $G \subseteq \as n$ (rather than $G \subseteq (\ps 1)^n$).

We fix a morphisms of $G$-quotient stacks $f\colon \stack Y₂ → \stack Y₁$ over $\stack X$, induced by a $G$-equivariant morphism of schemes $f'\colon Y₂ → Y₁$.
Further let $h_i'\colon Y_i → X$ be the structure maps.
According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working directly with the stacks, we can base change to schemes.
We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the primes and the \enquote{$\stack Y$} from the maps.
The following diagram summarizes all the spaces and maps that we need to consider.
\[
    \begin{tikzcd}
        Γ \arrow[d, hook, "j"] & & \slsY[\stack Y₁]{\stack X} \arrow[d, hook, "j₁"] & \\
        \bar Γ & \scls{\stack X} \arrow[l, "\bar p₂"'] & \sclsY[\stack Y₁]{\stack X} \arrow[l, gray, "\scls{h₁}"'] & \sclsY[\stack Y₂]{\stack X} \arrow[l, "\scls{f}"'] \\
        & \slsc{\stack X} \arrow[u, hook, "i"] &  & \slscY[\stack Y₂]{\stack X} \arrow[u, hook, "i₂"]
    \end{tikzcd}
\]
We want to show that our usual push-pull operations vanish along the two zig-zags (for $G×G$-mododromic holonomic D-modules).
To unify notation, let us set $Y₀ = X$ and $h_0 = \id[X]$

The general idea is now to introduce $\Gm$-actions that contracts $\sclsY[\stack Y_i] \stack X$ onto $\slscY[\stack Y_i] \stack X$.
In order to do so, we will cut the schemes
\[
    \sclsY[\stack Y_i] \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ
    \biggr\}
\]
into pieces according to the subgroups of $G$ that stabilize $h_i(y)$.
For this let $\Stab\stack X$ be the set of all closed subgroups of $G$ that are stabilizers of points of $X$, i.e.
\[
    \Stab\stack X = \bigl\{ G_x : x ∈ X \bigr\}.
\]

@@

\begin{proof}
    Since $X$ is affine, it can be embedded $G$-equivariantly into some $\as m$ with a linear $G$-action.
    For $\as m/G$ the statement is easy to see.
\end{proof}

\begin{Rem}\label{rem:why_locally_linear}
    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
    Thus it would suffice to assume in Theorem~\ref{thm:torus:is-good} that $X$ can be covered by open subschemes for which Lemma~\ref{lem:finitely_many_stabilizers} holds.
\end{Rem}

Let $S$ be closed subgroup of $G$ and let $X^S$ be the $S$-fixed points of $X$.
Since $G$ is Abelian (and hence $S$ a normal subgroup), $X^S$ is a $G$-stable closed subscheme of $X$.
Hence $X^S/G$ is a closed substack of $\stack X$.
Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the closed subspace
\[
    \stabclsY[\stack Y_i]{S}{\stack X} =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^S,\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
    \biggr\}
    ⊆
    \sclsY[\stack Y_i] \stack X.
\]

\begin{Lem}
    \label{lem:stabilizers_cover}%
    For $i \in \{0,1,2\}$, the subspaces $\stabclsY[\stack Y_i]{S}{\stack X}$ for $S ∈ \Stab\stack X$ cover $\sclsY[\stack Y_i]{\stack X}$.
\end{Lem}

\begin{proof}
    Consider the spaces
    \[
        \stablsY[\stack Y_i]{S}{\stack X} =
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × G : h_i(y) ∈ X^S,\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ Γ \text{ and } g₂ ∈ g₁S
        \biggr\}
        \subseteq \slsY[\stack Y_i] \stack X.
    \]
    The closure of $\stablsY[\stack Y_i]{S}{\stack X}$ in $\sclsY[\stack Y_i] \stack X$ is exactly $\stabclsY[\stack Y_i]{S}{\stack X}$.
    It is easy to see that the subspaces $\stablsY[\stack Y_i]{S}{\stack X}$ for $S ∈ \Stab \stack X$ cover $\slsY[\stack Y_i] \stack X$.
    Now the statement follows from the fact that the closure of a finite union is the union of the individual closures.
\end{proof}

The upshot of this is that we can check vanishing by restricting to all $\stabclsY[\stack Y_i]{S}{\stack X}$.
However, since these spaces are closed we will need to make use of a Mayer--Vietoris argument.
Thus we need to also consider intersections of these schemes.
For this let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$ and set
\[
    \stabclsY[\stack Y_i]{S₁,S₂} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
    \biggr\}.
\]
Clearly we have $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \subseteq \stabclsY[\stack Y_i]{S₁}{\stack X}$ and $\stabclsY[\stack Y_i]{S}{\stack X} = \stabclsY[\stack Y_i]{S,S}{\stack X}$.
Similarly, we set
\[
    \bar Γ^{S₁,S₂} = \bigl\{ (g,x,y) ∈ \bar Γ : x ∈ X^{S₂} \text{ and there exists $g' ∈ G$ such that $g ∈ g'S₁$}  \bigr\}.
\]
As in Lemma~\ref{lem:stabilizers_cover} one sees that the closed subschemes $\bar Γ^{S,S}$ cover $\bar Γ$.
Denote the inclusions by
\[
    α_i^{S₁,S₂}\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \hookrightarrow \sclsY[\stack Y_i]{\stack X}
    \qquad\text{and}\qquad
    α_{-1}^{S₁,S₂}\colon \bar Γ^{S₁,S₂} \hookrightarrow \bar Γ.
\]
We are now ready to formulate the main technical lemma of this section.
It will allow us to cut up our spaces into pieces on which we have control over the sheaves of interest.

\begin{Lem}\label{lem:torus:key}
    Fix any $S₁ ⊆ S₂$ in $\Stab\stack X$ and a component $H$ of $\bar G \setminus G$ (hence $H$ is a hyperplane of $\as n$).
    Write $Z_i$ for the closed subschemes of $\slscY[\stack Y_i]\stack X$ with $g₂ ∈ H$, and similarly $Z_{-1} = \bar Γ ∩ H × X × X$.
    Consider the Cartesian diagrams
    \begin{equation}\label{eq:lem:torus:key:cartesian}
        \begin{tikzcd}
            Z₂ \arrow[r, hook, "i₂^H"] \arrow[d, "\scls f^H"] & \sclsY[\stack Y₂]{\stack X} \arrow[d, "\scls f"] \\
            Z₁ \arrow[r, hook, "i₂^H"] & \sclsY[\stack Y₁]{\stack X}
        \end{tikzcd}
        \qquad\text{and}\qquad
        \begin{tikzcd}
            Z₀ \arrow[r, hook, "i₀^H"] \arrow[d, "\bar p₂^H"] & \scls{\stack X} \arrow[d, "\bar p₂"] \\
            Z_{-1} \arrow[r, hook, "i_{-1}^H"] & \bar Γ
        \end{tikzcd}. 
    \end{equation}
    Then the canonical morphisms [Write up the morphisms?]
    \[
        i^{H,*}_0 α_{0,*}^{S₁,S₂}α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
        →
        \bar p₂^{H,!} i^{H,*}_{-1} α_{-1,*}^{S₁,S₂}α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
    \]
    and
    \[
        i^{H,*}_2 α_{2,*}^{S₁,S₂}α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
        →
        {\scls f}^{H,!} i^{H,*}_1 α_{1,*}^{S₁,S₂}α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
    \]
    are isomorphisms for any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ and $\sheaf G ∈ \catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
\end{Lem}

Before proving the lemma, let us first finish the proof of Theorem~\ref{thm:torus:is-good}, assuming the Lemma.

\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
    We have to prove that 
    \[
        i₀^* \bar p₂^! j_{!} \sheaf F = 0
        \qquad\text{and}\qquad
        i₂^{*} {\scls f}^! j_{1,!} \sheaf G = 0
    \]
    for any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ and $\sheaf G ∈ \catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
    Let $H$ be a component of $\bar G \setminus G$, i.e.~one of the coordinate hyperplanes of $\as n$.
    It suffices to prove that 
    \[
        i₀^{H,*} \bar p₂^! j_{!} \sheaf F = 0
        \qquad\text{and}\qquad
        i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G = 0
    \]
    for any such $H$.
    We will prove the second of these statements.
    The first follows in exactly the same way, using $\bar Γ$ and $\scls\stack X$ instead of $\sclsY[\stack Y₁]{\stack X}$ and $\sclsY[\stack Y₂]{\stack X}$.
    The idea is to compare the above sheaves each with a sheaf that is evidently zero by cutting the space into pieces and using Mayer--Vietoris triangles.

    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\stabclsY[\stack Y_i]{S}\stack X$ for $S ∈ \Stab \stack X$ cover $\sclsY[\stack Y_i]{\stack X}$.
    If $S₁,\, S₂ ∈ \Stab\stack X$, then
    \[
        \stabclsY[\stack Y_i]{S₁}{\stack X} ∩ \stabclsY[\stack Y_i]{S₂}{\stack X} =
        \stabclsY[\stack Y_i]{S₁∩S₂,\, S₁S₂}\stack X.
    \]
    Thus, using the notation of diagram~\eqref{eq:lem:torus:key:cartesian}, we can use Mayer--Vietoris triangles to write $i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G$ as an iterated extension of (direct sums of) sheaves of the form
    \[
        i^{H,*}_2 α_{2,*}^{S₁,S₂}α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G, \qquad S₁ ⊆ S₂ ∈ \Stab \stack X.
    \]
    Similarly we can write ${\scls f}^{H,!} i^{H,*}_1 j_{1,!}$ as an iterated extension of
    \[
        {\scls f}^{H,!} i^{H,*}_1 α_{1,*}^{S₁,S₂}α₁^{S₁,S₂,!} j_{1,!} \sheaf G, \qquad S₁ ⊆ S₂ ∈ \Stab \stack X.
    \]
    We have canonical maps between each of the sheaves in these triangles.
    By Lemma~\ref{lem:torus:key} each of them, except possibly between the original sheaves, are isomorphisms.
    But then also the canonical map
    \[
        i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G → {\scls f}^{H,!} i^{H,*}_1 j_{1,!} \sheaf G
    \]
    is an isomorphism.
    Finally, ${\scls f}^{H,!} i^{H,*}_1 j_{1,!} \sheaf G$ mush vanish, as $i^{H,*}$ can be factored through the $*$-restriction to $\slscY[\stack Y₁]{\stack X}$.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lem:torus:key}]
    The schemes $\stablscY[\stack Y_i]{S₁,S₂}{\stack X} = \slscY[\stack Y_i]{\stack X} ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ are given by
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
        \biggr\}.
    \]
    Set $H' = H ∩ \bar S₁$ and $Z_i' = Z_i ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$Z_{-1}' = Z_{-1} ∩ \bar Γ^{S₁,S₂}$).
    These schemes can be described as
    \[
        Z_i'
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H'
        \biggr\}.
    \]
    and similarly for $Z_{-1}'$.
    If $H' = \emptyset$ then the $Z_i'$ are empty and the statements of the lemma are trivially true.
    Thus assume that $H'$ is not empty.
    Let $i_i^{H'}$ be the inclusion of $Z_i'$ into $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$\bar Γ^{S₁,S₂}$).
    We have to show that the canonical maps
    \[
        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
        →
        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
    \]
    and
    \[
        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
        →
        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
    \]
    are isomorphisms.

    We will do so by using the Contraction Principle of Theorem~\ref{thm:pre:contraction_principle}.
    For this we will introducing a contractive $\Gm$-action on $\bar Γ$ and all $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ such that the morphisms
    \begin{equation}
        \label{eq:torus:middle_row}
        \begin{tikzcd}
            \bar Γ^{S₁,S₂} &
            \stabcls{S₁,S₂}{\stack X} \arrow[l, "\bar p₂"'] &
            \stabclsY[\stack Y₁]{S₁,S₂}{\stack X} \arrow[l, "\scls{h₁}"'] &
            \stabclsY[\stack Y₂]{S₁,S₂}{\stack X} \arrow[l, "\scls{f}"']
        \end{tikzcd}
    \end{equation}
    are $\Gm$-equivariant (where we abuse notation to denote the restrictions of the morphisms with the same name).

    We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
    This gives a corresponding decomposition of the monoid $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
    Chose an action $μ$ of $\Gm$ on the identity component of $\bar S₁$ that contracts $\bar S₁$ onto $H'$ .
    This induces an action of $\Gm$ on $\bar G = \bar G₁ \bar S₁$ by $u \cdot ts = tμ(u,s)$, contracting $\bar G$ to (a closed subset of) $H$.

    In turn this action induces contractive actions on $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ and $\bar Γ^{S₁,S₂}$.
    We write 
    \[
        π_i\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} → Z_i'
        \qquad\text{and}\qquad
        π_{-1}\colon \bar Γ^{S₁,S₂} → Z_{-1}'
    \]
    for the corresponding contraction morphisms.

    We note that all D-modules are monodromic with respect to these $\Gm$-actions.
    Thus we can apply the contraction principle and base change to obtain the canonical isomorphisms
    \[
        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F =
        π_{0,*} \bar p₂^! α_{-1}^{S₁,S₂,!} j_{!} \sheaf F =
        \bar p₂^{H',!} π_{-1,*} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F =
        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
    \]
    and
    \[
        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G = 
        π_{2,*} {\scls f}^! α₁^{S₁,S₂,!} j_{1,!} \sheaf G = 
        {\scls f}^{H',!} π_{1,*} α₁^{S₁,S₂,!} j_{1,!} \sheaf G = 
        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G
    \]
    as required.
\end{proof}
